---
title: "Using s6model to assess the status of North Sea cod (cod-347d)"
author: "Alexandros Kokkalis"
date: "`r Sys.Date()`"
output: 
#  rmarkdown::html_vignette:
#    fig_caption: yes
  pdf_document:
    toc: true
    highlight: default
# bibliography: bib.bibtex
vignette: >
  %\VignetteIndexEntry{Using s6model to assess the status of North Sea cod (cod-347d)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

The North Sea cod (_Gadus morhua_) is assessed in this example using only survey data from the NS-IBTS survey. The data can be downloaded from the [DATRAS](http://datras.ices.dk) database. 

## Downloading and pre-processing of the data

The data are downloaded using the `DATRAS` package which can be installed using:
```{r, eval=FALSE, echo = TRUE}
install.packages('DATRAS',repos='http://www.rforge.net/',type='source')
```

The package contains functions to download, read and subset survey data. Shape files for ICES regions can be downloaded from [ICES spatial facility](http://geo.ices.dk/).

```{r, echo = TRUE, eval = FALSE}
library(DATRAS)
## Download the survey data for the years 1991 to 2014
downloadExchange("NS-IBTS", 1991:2014)
## Read in all data
nsibts <- readExchangeDir()
## Select only cod
nscod <- subset(nsibts, Species == "Gadus morhua")
```

Select only the relevant areas for the North Sea Baltic cod
```{r, echo=TRUE, eval = FALSE}
## Add area information
nscod <- addSpatialData(nscod, shape = "ices_areas.shp")
nscod <- subset(nscod, ICES_area %in% c("IIIa", "IVa", "IVb", "IVc", "VIId"))
```

Then using the `s6model` package we can extract the yearly weight frequencies using the function `getDFYears`. This function extracts the length distributions from an object of class `DATRASraw`, fits the weight length relationship, transforms the length to weight and returns a `list` of `data.frames`, one for each year. The bin size is set to 100 g (`binsize` argument) and the weight-length relationship is fitted using weight and length data in the survey for each year (`estWL` argument).
```{r, echo = TRUE, eval = FALSE}
library(s6model)
nscoddat <- getDfYears(nscod, binsize = 100, estWL = TRUE)
```

Now the data are in a format that can be used to assess the stock status. The data are provided with the package (saved as `nscoddat`).

## Assessment of the stock

Now the data are in the correct format the assessment can be done using the `makeAssessment` function. It has many arguments and only a subset of them are presented here. There are default values for most of them, so that a preliminary assessment can be done using `makeAssessment(dat)`, where `dat` has the data in the correct format. The results are saved after a successful run of the function so that they can accessed at a later point to make plots and reports.

Since it is an assessment using only survey data, we are using `isSurvey = TRUE` and we make the assumption that all sizes are selected by the gear by setting the relative selectivity parameter ($\eta_S$, argument `eta_S`) of the gear very small. The results are not saved (`fnout = NULL`). The default values for mean and sd of physiological mortality from @Kokkalis2015 are used.
```{r assessment, echo=TRUE, message=FALSE, warning=FALSE, cache=TRUE}
library(s6model)
yrs <- s6model:::getYears(names(nscoddat))
w <- ices.cod[["cod-347d"]]$Year %in% yrs
land <- ices.cod[["cod-347d"]]$Landings[w]
res <- makeAssessment(nscoddat, fnout = NULL, isSurvey = TRUE, eta_S = 1e-3, yield = land, u = NULL,
                      a = 0.22, a.sd = 0.7, nsample = 20, binsize = 500)
```


## Reporting the results

The results of the assessment of $F/F_{msy}$ are plotted using `plot` function. The y-axis is in log-scale and its limits are set.
```{r plotting, echo = TRUE, eval = TRUE, cache = TRUE, dependson="assessment"}
par(mar = c(3.1, 3.1, 0.1, 0.1))
plot(res, ylim = c(1/15,15), log = "y")
addIces("cod-347d", col = "lightgrey")
plot(res, what = "ssb", ylim = c(1, 150), mult = 1000)
addIces("cod-347d", mult = 1/1000, what = "SSB")
```


