---
title: "Using s6model to assess the status of Nephrops (FU 23-24, nep-2324)"
author: "Alexandros Kokkalis"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
# bibliography: bib.bibtex
vignette: >
  %\VignetteIndexEntry{Using s6model to assess the status of Nephrops (FU 23-24, nep-2324)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette will show a complete example of a complete workflow using _s6model_, going from catch-at-length data, pre-processing them, doing the actual assessment and report the results. The case study is about Nephrops (_Nephrops norvegicus_) in functional units 23-24 Bay of Biscay (VIIIa,b, nep-2324). Available data of landings length distributions from the years 1987--2014 from the ICES WGBIE report (@ICES2015) are included in the package and can be accessed using.

## Pre-processing of the data

The first step is to read in the data from the two csv files included in the `s6model` package in the folder *nep-2324*.

```{r, echo = TRUE}
fn <- system.file("nep-2324","nep2324_catch1987_2014.csv", package = "s6model")
nepdat <- read.table(fn, sep = ",", header = TRUE)
```

The first collumn (`Lmm`) is the lenght in mm, the rest are one for each year. The numbers are in thousends. The first 6 rows and 12 columns are presented in the following table.
```{r, echo=FALSE}
knitr::kable(head(nepdat[, 1:15]))
```

<!-- Use `DATRAS` package to download and read exchange data from the EVHOE survey. -->
<!-- ```{r, echo = TRUE} -->
<!-- library(DATRAS) -->
<!-- ## Download all years of EVHOE survey -->
<!-- downloadExchange("EVHOE") -->
<!-- ## Read in all data -->
<!-- evhoe <- readExchangeDir() -->
<!-- nepevhoe <- subset(evhoe, Species == "Nephrops norvegicus") -->
<!-- nepevhoe <- addSpectrum(nepevhoe) -->
<!-- fitWL(nepevhoe) -->
<!-- ``` -->


## Assessment of nep-2324

## Presenting the results

## References
